\rule{\textwidth}{4pt}\\[1em] \textbf{From Distribution Forecasts to Vanilla Portfolios: \\[0.2cm] Regularized Payout Approximation in Discrete Space}\\[1em] \rule{\textwidth}{2pt}

### 2025-02-14 latex/article.tex
Carr-Madan reference

\section{Literature Review}

>>>>

\section{Literature Review}
The theoretical foundations of option portfolio optimization were established by 
\cite{Carr01012001}, who demonstrated the theoretical possibility of replicating 
arbitrary payout functions through continuous strike spaces. While their approach 
provides elegant closed-form solutions in continuous market settings, three fundamental 
limitations hinder practical implementation: the discrete availability of strike prices 
in real markets, liquidity constraints, non-negligible transaction costs scaling with 
portfolio complexity, and numerical stability challenges in finite difference implementations. 
Proposed method addresses these limitations through regularization techniques and 
discrete optimization methods tailored for real-world trading environments, while 
preserving the theoretical elegance of the original framework.
